Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-04-12 paper/AlignedIsotropicGW.tex
Formatting
Added Nature statements about author contributions, etc.

\email{w.farr@bham.ac.uk, simons@star.sr.bham.ac.uk, miller@astro.umd.edu,\\imandel@star.sr.bham.ac.uk, farr@uchicago.edu, av@star.sr.bham.ac.uk}

@@

@@

>>>>

\email{w.farr@bham.ac.uk, simons@star.sr.bham.ac.uk, miller@astro.umd.edu,\\
imandel@star.sr.bham.ac.uk, farr@uchicago.edu, av@star.sr.bham.ac.uk}

@@

Supplementary Information is linked to the online version of the paper
at \url{http://www.nature.com/nature}.

@@

All authors contributed to the work presented in this paper.

Reprints and permissions information is available at
\url{http://www.nature.com/reprints}.

The authors declare no competing financial interests.

Correspondence and requests for materials should be addressed to
\href{mailto:w.farr@bham.ac.uk}{w.farr@bham.ac.uk}.
